\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{Reflection Report on Pot-pulator}
\title{Reflection Report on Pot-pulator}

\author{Team \#24, The Nursery Project\\Aaron Billones, billonea\\Gillian Ford, fordg\\Juan Moncada, moncadaj\\Steven Ramundi, ramundis}
\date{April 5, 2023}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

% \plt{Reflection is an important component of getting the full benefits from a
% learning experience.  Besides the intrinsic benefits of reflection, this
% document will be used to help the TAs grade how well your team responded to
% feedback.  In addition, several CEAB (Canadian Engineering Accreditation Board)
% Learning Outcomes (LOs) will be assessed based on your reflections.}

\section{Changes in Response to Feedback}

% \plt{Summarize the changes made over the course of the project in response to
% feedback from TAs, the instructor, teammates, other teams, the project
% supervisor (if present), and from user testers.}

% \plt{For those teams with an external supervisor, please highlight how the feedback 
% from the supervisor shaped your project.  In particular, you should highlight the 
% supervisor's response to your Rev 0 demonstration to them.}

\subsection{SRS and Hazard Analysis}

Changes were made to SRS based on feedback from teammates, the instructor, and TAs. 
Requirements were adjusted as the design and scope of the project changed.

\subsection{Design and Design Documentation}

Design underwent many major changes throughout the process based on feedback. Between Proof of Concept 
and Rev0 Demo, feedback from teammates influenced a major change in the final design of the tray dropper 
subsystem. After Rev0, feeback from the instructor and TA influenced the revised design of the pot dropper 
subsystem, increasing the accuracy of the machine overall.

\subsection{VnV Plan and Report}

The VnV Plan and Report changed based on feedback from peers. Testing plans were updated to better ensure all 
components of the machine were being tested thoroughly, and all edge cases were considered when conducting testing.
\section{Design Iteration (LO11)}

The design process of the Pot-pulator went through various iterations.
Our initial design for inserting the pots into the trays consisted of 
actuators that would place the pots inside the slots. While this solution 
is more precise and robust than our final solution, it requires very expensive
materials in order to have it fully operational. After confirming our design for dispensing the pots,
there were iterations with our 3-D printed parts that improved with each iteration.
At first the thread in the disc was too wide where the device would drop multiple pots at one time.
Therefore, we went through several design iterations in order to achieve the correct part design.\\\\

\noindent Similar to the pot dispenser, the tray dispenser design had been through multiple iterations.
Initially, we were going to use and gantry system to move the trays from a stack to the conveyor belt.
We soon came to realize that this solution would also be very expensive and lacking the time/materials in 
order to obtain a working final solution. After we iterated through our gear design which drops the trays
from a stack above the conveyor one at a time. This also took some iterating as we needed to ensure that only one tray 
would be dropped when we want it to.

\section{Design Decisions (LO12)}

With our project being more of a physical solution rather than a software one, 
there were many assumptions made and a lot more constraints pressed upon us.
For example, the 750 dollar budget limited us to changing some of our designs because some initial ones were too expensive.
Some assumptions made were that the area would be clean and weather would not affect our device.
Weather proofing our device would cost more money and materials that we did not have access to.
We also should have made more timely design decisions as there were many instances where we were falling behind.
More timely design goals should have been set which would help our overall design process and success in the project.

\section{Economic Considerations (LO23)}

% \plt{Is there a market for your product? What would be involved in marketing your 
% product? What is your estimate of the cost to produce a version that you could 
% sell?  What would you charge for your product?  How many units would you have to 
% sell to make money? If your product isn't something that would be sold, like an 
% open source project, how would you go about attracting users?  How many potential 
% users currently exist?}

We believe there is a market for our product. All Sheridan Nurseries farms are ran in the same way 
as the farm which we used to influence our design. The cost of the manual labour does not justify the 
purchase of the machines that are currently available on the market, but our low cost solution is perfect 
for Sheridan Nurseries' current situation. It is also a great solution for any industrial potting farm which 
owns a soil and seed filling machine, but does not own a pot and tray sorting machine. Marketing the product 
would involve giving live demonstrations to decision makers at the farms or distributing videos showcasing the functionality 
of the machine and highlighting the value it will provide. We estimate it would cost approximately \$700 to manufacture 
if our current sourcing methods are used, but this price can be drastically reduced if it were to be manufactured in large 
quantities. We would charge a price which would translate to a 60\% markup. At a cost of \$700, this would mean setting the price 
at approximately \$1150. We would be making about \$450 per machine, and our break even point would be dependent on the amount of 
capital we would be required to invest to establish a manufacturing process, and the amount of fixed costs that would incur on other 
activities such as advertising.

\section{Reflection on Project Management (LO24)}

\plt{This question focuses on processes and tools used for project management.}

\subsection{How Does Your Project Management Compare to Your Development Plan}

\plt{Did you follow your Development plan, with respect to the team meeting plan, 
team communication plan, team member roles and workflow plan.  Did you use the 
technology you planned on using?}

\subsection{What Went Well?}

\plt{What went well for your project management in terms of processes and 
technology?}

\subsection{What Went Wrong?}

\plt{What went wrong in terms of processes and technology?}

\subsection{What Would you Do Differently Next Time?}

\plt{What will you do differently for your next project?}

\end{document}